---
title: "Lab4"
author: "Sam SIlva"
date: "2/12/2020"
output: html_document
---

```{r}
library(tidyverse)
SNPs<- read.table("23andMe_complete.txt", header = TRUE, sep = "\t")
```

```{r}
### Exercise 1
SNPs$chromosome = ordered(SNPs$chromosome, levels=c(seq(1,22), "X","Y","MT"))
ggplot(SNPs, aes(chromosome))+
geom_bar(color="blue", fill="blue") + 
  ggtitle("Total SNPs for each Chromosome") 
```


```{r}
### Exercise 2
ggplot(SNPs, aes(chromosome, fill = genotype))+
geom_bar()+
  ggtitle("Total Number of SNPs for each Chromosome")+
  ylab("Number of SNPs")+
  xlab("Chromosome Number")+
  scale_fill_manual(values = c("AA"="red","CC"="red","GG"="red","TT"="red","AC"="red","AG"="red","AT"="red","CG"="red","CT"="red","GT"="red","A"="blue","C"="blue","G"="blue","T"="blue","D"="green","DD"="green","DI"="green","II"="green","I"="green","--" = "green"))

```

```{r}
### Exercise 3
ppi <- 300
png("SNP_plot.png",width = 6*ppi, height = 6*ppi, res=ppi)
ggplot(SNPs, aes(chromosome, fill = genotype))+
geom_bar(position="dodge2")+
  ggtitle("Total Number of SNPs for each Chromosome")+
  ylab("Number of SNPs")+
  xlab("Chromosome Number")+
  scale_fill_manual(values = c("AA"="red","CC"="red","GG"="red","TT"="red","AC"="red","AG"="red","AT"="red","CG"="red","CT"="red","GT"="red","A"="blue","C"="blue","G"="blue","T"="blue","D"="green","DD"="green","DI"="green","II"="green","I"="green","--" = "green"))
dev.off()
```

``````{r}
### Exercise 4
ggplot(SNPs, aes(chromosome, fill = genotype))+
geom_bar(position="dodge2")+
facet_wrap(~genotype,ncol = 2, scales = "free_y")+
   ggtitle("Total Number of SNPs for each Chromosome")+
  ylab("Number of SNPs")+
  xlab("Chromosome Number")+
  scale_fill_manual(values = c("AA"="red","CC"="red","GG"="red","TT"="red","AC"="red","AG"="red","AT"="red","CG"="red","CT"="red","GT"="red","A"="blue","C"="blue","G"="blue","T"="blue","D"="green","DD"="green","DI"="green","II"="green","I"="green","--" = "green"))
```

```{r}
library(plotly)
```

```{r}
### Exercise 5
ggplotly()
ggplot(SNPs, aes(chromosome, fill = genotype))+
geom_bar(position="dodge2")+
facet_wrap(~genotype,ncol = 2, scales = "free_y")+
   ggtitle("Total Number of SNPs for each Chromosome")+
  ylab("Number of SNPs")+
  xlab("Chromosome Number")+
  scale_fill_manual(values = c("AA"="red","CC"="red","GG"="red","TT"="red","AC"="red","AG"="red","AT"="red","CG"="red","CT"="red","GT"="red","A"="blue","C"="blue","G"="blue","T"="blue","D"="green","DD"="green","DI"="green","II"="green","I"="green","--" = "green"))
```

```{r}
library(DT)
```

```{r}
### Exercise 6
datatable(head(SNPs), class = "Y Chromosome")
```

